---
title: "Chapter 10 Lab"
author: "I 'State Your Name'" #Put your name here, but don't change the other lines in this 'YAML' section of the document
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
---

WHEN READING CHAPTER 10, STOP AT THE END OF 10.6.

YOU DO NOT NEED TO READ SECTION 10.7 OR 10.8.


You can read more about [R Markdown](http://rmarkdown.rstudio.com) Notebooks. 

Run this chunk to install and/or load rmarkdown (Remember, you can  run this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter* or by pressing the green arrow in the upper right of the chunk.)

```{r}
#install.packages("rmarkdown")
library("rmarkdown")

pacman::p_load(lubridate, dplyr, Hmisc,testthat)

```


*After each question, run the chunk to check your code.*

# 1.	Write a function called "printToday" that prints "Today is" and the current date. Then run it on a separate line.
```{r}
printToday <-function(){
  my_text <- paste0("Today is ",Sys.Date())
  print(my_text)
}

printToday()
```


# 2. Write a function called "printFuture" that prints "Today plus", followed by x number of days, followed by "days is", followed by the system data in x days. Then run that function on a separate line.
```{r}
printFuture <-function(x){my_text <-paste0("Today plus ",x," days is ", Sys.Date()+x)
print(my_text)
}

printFuture(7)
```


# 3. Write a function called "printFuture2" for which the default value of x is tomorrow's date.
```{r}
printFuture2 <-function(x =1){
  my_text <- paste0("Today plus ", x, " days is ", Sys.Date() + x )
}


```


# 4. Write a function called "get_first_of_last_month that, well, returns the first date of last month.
```{r}
get_first_of_last_month <- function(mydate = Sys.Date()) {
  mydate <- mydate - months(1)
  mydate <- cut(mydate, "month")
  return(mydate)
}

get_first_of_last_month()
```


# 5. Use the `seq()` function to return a list of the first 7 days in August 2020.
```{r}
seq.Date(as.Date("2020-08-01"),length.out = 7,by="day")
```


# 6. Write a function to get the last day of last month.
```{r}
get_last_of_last_month <- function(mydate = Sys.Date()) {
  mydate <- mydate - months(1)
  mydate <- cut(mydate, "month")
  seq.Date(as.Date(mydate),length.out = 30,by = "day")
}
x

```


# 7. Write a function called "get_last_Monday" that returns seven days before today's date if today is a Monday, eight days before today's date if today is a Tuesday and the warning message "You are running this script on a day that wasn't Monday or Tuesday." if today is not a Monday or a Tuesday. Then run that function on a separate line.
```{r}
get_last_Monday <-function(today = Sys.Date()){
today <- Sys.Date() 
if(weekdays(today) == "Monday") { 
  lastMonday <- today - 7  
} else if(weekdays(today) == "Tuesday") { 
    lastMonday <- today - 8  
} else { 
lastMonday <- warning("You are running this script on a day that isn't  Monday or Tuesday. Results will not be accurate.  Please calculate the date for last Monday manually.") } 
}

 get_last_Monday()
```


# 8. Now write a function called "get_last_Monday2" that always prints the Monday before the most recent Monday.
```{r}
I really could not figure this one out. 
```


# 8. Create a function that uses the numeric weekday values to return the date for "Monday of last week," accounting for possibilities for all seven weekdays -- without explicitly writing out each case.
```{r}
get_last_Monday <- function(the_day = Sys.Date()){ 
  today <- weekdays(the_day) 
  my_result <- dplyr::case_when(  
    today == "Monday" ~ the_day - 7, 
    today == "Tuesday" ~ the_day - 8, 
    today == "Wednesday" ~ the_day - 9,
    today == "Thursday" ~ the_day - 10, 
    today == "Friday" ~ the_day - 11, 
    today == "Saturday" ~ the_day - 12,  
    today == "Sunday" ~ the_day - 13  
    )  
  return(as.character(my_result)) 
}

get_last_Monday()
```


# 9. Use R's ifelse() function to write a function called "IsItOdd" that tests whether any number in a vector of numbers is odd or even.
```{r}
IsItOdd <- function(thenumber) {  
  result <- ifelse(thenumber %% 2 == 1, "Odd", "Not odd")  return(result)  
  } 


```


You can stop at the end of section 10.6. But if you would like to show me that you did some work on sections 10.7 or 10.8, I can give you two extra credit Lab points.



# Run, Knit and Submit
When you've finished, use the "Preview" pulldown menu at the top of this pane to select "Knit to HTML". This will save an HTML file to this project's directory. 

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

After you've created the HTML file of your answers, you can Stage, Commit and then push your .Rmd and .html files back to GitHub where I will grade them.

